conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-23 paper/paper.Rmd
Improved explanation for model fitting

`conmat` was built to predict at four settings: work, school, home, and other. 
The model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants. The model has six (?)covariates/terms to explain six key features of the relationship between ages, and two optional terms for attendance at school or work. The two optional terms are included depending on which setting the model is fitted for. There are four resulting models, with one model fitted for each setting.

>>>>

`conmat` was built to predict at four settings: work, school, home, and other. 
One model is fitted for each setting. 
Each model fitted is a Poisson generalised additive model (GAM) which predicts the count of contacts, with an offset for the log of participants. 
The model has six (?)covariates/terms to explain six key features of the relationship between ages, 
and two optional terms for attendance at school or work.
The two optional terms are included depending on which setting the model is fitted for.
